Microbial interactions as drivers of a nitrification process in a chemostat

### 2020-04-09 tex/Article_Interactions.tex
modified tex
word change

\author{Pablo Ugalde-Salas, Jérôme Harmand, Elie Desmond Le-Quéméner, Héctor Ramirez}
\date{}
\maketitle

@@

In section 4 the concept of interaction function is developed such that it generalizes the gLV model. For the identification of the interaction function a method of optimal control theory was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected in order to fit the experimental data. The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species; the method involves solving state-dependent Ricatti equations\cite{Cimen2008}.

>>>>

\author{Pablo Ugalde-Salas, Héctor Ramirez C., Jérôme Harmand, Elie Desmond-Le Quéméner}
\date{}
\maketitle

@@

In section 4 the concept of interaction function is developed such that it generalizes the gLV model. For approximating the interaction function a method of optimal control theory was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected in order to fit the experimental data. The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species; the method involves solving state-dependent Ricatti equations\cite{Cimen2008}.
